---
title: "Predicting Miles per Gallon"
author: "Daniel Arturo Lopez Sanchez"
date: "11/10/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This is the Developing Data Products Final Project. The main idea is to predict the mileage of a car, given 4 predictors.This predictors are:

- Number of cylinders
- Gross horsepower
- whether if the car's transmission type is automatic or manual
- Weight

You'll need to input these values and the result will be the predicted miles per gallon.

## Summary of the model

```{r model, echo=FALSE }
mtcars$cyl <- factor(mtcars$cyl)
mtcars$am <- factor(mtcars$am)
model1 <- lm(formula = mpg~cyl+hp+wt+am, data = mtcars)
summary(model1)
```

## Summary of the variables

Miles per gallon, horsepower and weight are numeric continuous variables. Number of cylinders and transmission type(am) are factors.
```{r mtcars, echo = FALSE}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$am <- factor(mtcars$am)
summary(mtcars[,c(1,2,4,6,9)])
```

## Interaction between variables

In this the upper panel of a scatter plot matrix. We can see some trends in the 4 predictors interacting with mpg.
```{r pairs, echo=FALSE}
pairs(mtcars[,c(1,2,4,6,9)], pch=19, lower.panel = NULL)
```

## Link to shiny app

https://daniellopezsnchz.shinyapps.io/predicting_mpg_model/







